Pillar 1 - Sequential Pattern Mining

### 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
created cumulative gap transcript (8 -> 8,9,10 grades)

@@

probabilities_manipulated <- d_transcript %>%
  transmute(tmp_id=paste(`Student ID`,`Course ID`,Year_numerical,Period,`Number Repeated Attempt`,sep="_"),
            Round_grade= round(Grade,0))
student_set <- unique(probabilities_manipulated$tmp_id)

for student %in% student_set

>>>>

```{r, cache = TRUE}
tmp_distributed_transcript <- d_transcript %>%
  filter(!is.na(Grade), Grade>=0) %>%
  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
         Values = T)
#This is the transcript with cumulative error gap.
distributed_transcript <- spread(tmp_distributed_transcript, key = "Round_grade", value = Values #, fill = F
               )%>%
  mutate(g1  = g0|g1,
         g2  = g1|g2,
         g3  = g2|g3,
         g4  = g3|g4,
         g5  = g4|g5,
         g6  = g5|g6,
         g7  = g6|g7,
         g8  = g7|g8,
         g9  = g8|g9,
         g10 = g9|g10,
         ) %>%
  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
  select(-Gr_bool )%>%
  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
  select(-Trash) %>%
  mutate(Grade= as.numeric(Grade_new))%>% #can put this into Grade and have just one grade value.
  select(-Grade_new)%>%
  arrange(`Course ID`, `Student ID`)

```
#Condensing grade

@@
